% OverDrive pitch

\documentclass[aspectratio=169]{beamer}
\usetheme{metropolis}           % Use metropolis theme
\title{OverDrive - A Hardware Secure USB Drive}
\date{\today}
\author{Ryan Walker}
\institute{}
\begin{document}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Motivation}
\begin{itemize}
\item \textbf{Problem:}
	Journalist doing important work in dangerous countries risk indictment if their work is 
    discovered. Typically they will use an operating system called Tails, which resides on
    a USB drive. If this drive falls into the authorities hands, they may be declared guilty
    by possession.

\item \textbf{Existing Solution:}
   It's possible to encrypt the drive, or use a drive which require a hardware password.
   However both techniques look suspicious.

\item \textbf{Our Solution:}
    Overdrive aims to be as discreet as possible. When the user inserts the drive using a specific
    technique, the hardware will expose a second partition. If not, it will expose it's first
    partition. It looks just like an ordinary drive.
\end{itemize}
\end{frame}

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Overview}
\begin{itemize}
\item \textbf{What it is.}\\
BirdEar is a low cost, battery powered device designed to monitor local bird activity. 

\item \textbf{How it works.}\\
BirdEar is equipped with sensors, microphone and a microcontroller.
The device determines the species of the bird from the call using an embedded machine learning algorithm. 
\end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Using BirdEar}
\begin{itemize}
\item \textbf{How to use it.}\\
The device is designed to be attached to a tree and may be left in place for several weeks before having to change the battery.

\item \textbf{What you get.}\\	
Upon retrieval, the user can expect to see a timestamp, bird species, and any additional sensor data collected over the deployment of the device. 
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Final Remarks}
	Hopefully, BirdEar will serve as a valuable tool for studying birds. % fix?

	Thank you for your time!
\end{frame}
\end{document}

% Questions
% ---------
% 1) As is, would this be a useful tool?
% 2) (Page 1) Can you think of any additional applications? Are the listed applications relevant?
% 3) Does anything like this exist currently? If so, what are the shortcomings? What is the price point?
% 4) What would an ideal battery life be?
% 5) Any additional sensors?
% 6) Any remarks or additional features?
